### 2022-03-24 paper/output/document/thesis_0_abstract.tex
full send

%
\begin{isabellebody}%
\setisabellecontext{thesis{\isacharunderscore}{\isadigit{0}}{\isacharunderscore}abstract}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isatagtheory
%
\endisatagtheory
{\isafoldtheory}%
%
\isadelimtheory
%
\endisadelimtheory
%
\begin{isamarkuptext}%
AI agents are beginning to make decisions without human supervision in increasingly consequential 
contexts like healthcare, policing, and driving. These decisions are inevitably ethically tinged, 
but most AI agents navigating the world today are not explicitly guided by ethics.
Regulators, philosophers, and computer scientists are raising the alarm about the 
dangers of unethical artificial intelligence, from lethal autonomous weapons to criminal
sentencing algorithms prejudiced against people of color. These warnings are spurring interest in 
automated ethics, or the development of machines that can perform ethical reasoning. Prior work in 
automated ethics rarely engages with philosophical literature, despite its relevance to the 
development of responsible AI agents. If automated ethics draws on sophisticated philosophical
literature, its decisions will be more nuanced, precise, and consistent, but automating ethical theories is 
difficult in practice. Faithfully translating a complex ethical theory from natural language to the 
rigid syntax of a computer program is technically and philosophically challenging.

In this thesis, I present an implementation of automated Kantian
ethics that is faithful to the Kantian philosophical tradition. Given minimal factual background, my 
system can judge an agent's potential action as morally obligatory, permissible, or prohibited.
To accomplish this, I formalize Kant's categorical imperative, or moral rule,
in deontic logic, implement this formalization 
in the Isabelle/HOL theorem prover, and develop a testing framework to evaluate how well 
my implementation coheres with expected properties of Kantian ethics, as established in the literature. 
This testing framework demonstrates that my system outperforms two other potential implementations of 
automated Kantian ethics. I also use my system to derive philosophically sophisticated and nuanced 
solutions to two central controversies in Kantian literature: the permissibility of lying in the 
context of a joke and to a murderer asking about the location of their intended victim. Finally, I 
examine my system's philosophical implications, demonstrating that it can not only guide AI agents, but it can
also help academic philosophers make philosophical progress and augment the everyday ethical reasoning
that we all perform as we navigate the world. I contribute a working proof-of-concept implementation
of automated Kantian ethics capable of performing philosophical reasoning more mature than anything previously
automated. My work serves as one step towards the development of responsible, trustworthy artifical intelligence.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimtheory
%
\endisadelimtheory
%
\isatagtheory
%
\endisatagtheory
{\isafoldtheory}%
%
\isadelimtheory
%
\endisadelimtheory
%
\end{isabellebody}%
\endinput
%:%file=~/Desktop/cs91r/paper/thesis_0_abstract.thy%:%
%:%19=6%:%
%:%20=7%:%
%:%21=8%:%
%:%22=9%:%
%:%23=10%:%
%:%24=11%:%
%:%25=12%:%
%:%26=13%:%
%:%27=14%:%
%:%28=15%:%
%:%29=16%:%
%:%30=17%:%
%:%31=18%:%
%:%32=19%:%
%:%33=20%:%
%:%34=21%:%
%:%35=22%:%
%:%36=23%:%
%:%37=24%:%
%:%38=25%:%
%:%39=26%:%
%:%40=27%:%
%:%41=28%:%
%:%42=29%:%
%:%43=30%:%
%:%44=31%:%
%:%45=32%:%
%:%46=33%:%
%:%47=34%:%

>>>>

%
\begin{isabellebody}%
\setisabellecontext{thesis{\isacharunderscore}{\isadigit{0}}{\isacharunderscore}abstract}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isatagtheory
%
\endisatagtheory
{\isafoldtheory}%
%
\isadelimtheory
%
\endisadelimtheory
%
\begin{isamarkuptext}%
AI is beginning to make decisions without human supervision in increasingly consequential 
contexts like healthcare, policing, and driving. These decisions are inevitably ethically tinged, 
but most AI systems in use today are not explicitly guided by ethics.
Regulators, philosophers, and computer scientists are raising the alarm about the 
dangers of unethical artificial intelligence, from lethal autonomous weapons to criminal
sentencing algorithms prejudiced against people of color. These warnings are spurring interest in 
automated ethics, or the development of machines that can perform ethical reasoning. Prior work in 
automated ethics rarely engages with philosophical literature, despite its relevance to the 
development of responsible AI. If automated ethics draws on philosophical
literature, its decisions will be more nuanced, precise, and consistent, but automating ethical theories is 
difficult in practice. Faithfully translating a complex ethical theory from natural language to the 
rigid syntax of a computer program is technically and philosophically challenging.

In this thesis, I present an implementation of automated Kantian
ethics that is faithful to the Kantian philosophical tradition. Given minimal factual background, my 
system can judge a potential action as morally obligatory, permissible, or prohibited.
To accomplish this, I formalize Kant's categorical imperative, or moral rule,
in deontic logic, implement this formalization 
in the Isabelle/HOL theorem prover, and develop a testing framework to evaluate how well 
my implementation coheres with expected properties of Kantian ethics, as established in the literature. 
This testing framework demonstrates that my system outperforms two other potential implementations of 
automated Kantian ethics. I also use my system to derive philosophically sophisticated and nuanced 
solutions to two central controversies in Kantian literature: the permissibility of lying (a) in the 
context of a joke and (b) to a murderer asking about the location of their intended victim. Finally, I 
examine my system's philosophical implications, demonstrating that it can not only guide AI, but it can
also help academic philosophers make philosophical progress and augment the everyday ethical reasoning
that we all perform as we navigate the world. Ultimately, I contribute a working proof-of-concept implementation
of automated Kantian ethics capable of performing philosophical reasoning more mature than anything previously
automated. My work serves as one step towards the development of responsible, trustworthy artifical intelligence.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimtheory
%
\endisadelimtheory
%
\isatagtheory
%
\endisatagtheory
{\isafoldtheory}%
%
\isadelimtheory
%
\endisadelimtheory
%
\end{isabellebody}%
\endinput
%:%file=~/Desktop/cs91r/paper/thesis_0_abstract.thy%:%
%:%19=6%:%
%:%20=7%:%
%:%21=8%:%
%:%22=9%:%
%:%23=10%:%
%:%24=11%:%
%:%25=12%:%
%:%26=13%:%
%:%27=14%:%
%:%28=15%:%
%:%29=16%:%
%:%30=17%:%
%:%31=18%:%
%:%32=19%:%
%:%33=20%:%
%:%34=21%:%
%:%35=22%:%
%:%36=23%:%
%:%37=24%:%
%:%38=25%:%
%:%39=26%:%
%:%40=27%:%
%:%41=28%:%
%:%42=29%:%
%:%43=30%:%
%:%44=31%:%
%:%45=32%:%
%:%46=33%:%
%:%47=34%:%

### 2022-03-24 paper/output/document/thesis_1_intro.tex
full send

%
\begin{isabellebody}%
\setisabellecontext{thesis{\isacharunderscore}{\isadigit{1}}{\isacharunderscore}intro}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isatagtheory
%
\endisatagtheory
{\isafoldtheory}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsection{Introduction\label{intro}%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
As AI agents become more sophisticated and less dependent on humans, interest begins to mount
in the development of automated moral agents, or computers that can perform ethical reasoning. 
AI agents are making decisions in increasingly 
consequential contexts, such as healthcare, driving, and criminal sentencing, and therefore 
must perform ethical reasoning in order to navigate moral dilemmas. For example, self-driving
cars may face less extreme versions of the following moral dilemma: an autonomous vehicle approaching 
an intersection fails to notice pedestrians in the crosswalk until it is too late to brake. The car 
can either continue on its course, running over and killing three pedestrians, or it can swerve to 
hit the car in the next lane, killing the single passenger inside it. While this example is (hopefully) 
not typical of the operation of a self-driving car, every decision that such an AI agent makes, from 
avoiding congested freeways to carpooling, is morally tinged. Not only do AI agents routinely make decisions with 
ethical implications without explicitly performing ethical
reasoning, they often do so without human supervision. For example, the Alleghany Family Screening 
tool can automatically trigger an investigation into a potential case of child neglect, a decision that 
can uproot entire families and is known to be biased against poor people of color \citep{eubanks}. 
This motivates the need for automated ethics (also called machine ethics), 
or the development of machines that can perform robust, sophisticated ethical reasoning.

Machine ethicists recognize the need for automated ethics and have made both theoretical 
(\citep{moralmachine}, \citep{davenport}, \citep{moralmachineonline}, \citep{gabriel}) and practical progress 
(\citep{logicprogramming}, \citep{biology}, \citep{winfield}, \citep{delphi}) towards automating ethics. 
However, prior work in machine ethics using popular ethical theories like deontology (\citep{deon1}, \citep{deon2}), 
consequentialism (\citep{util2}, \citep{util1}, \citep{cloos}), and virtue ethics \citep{virtue2} rarely 
engages with philosophical literature and thus often misses philosophers' insights. Even the above example of 
the malfunctioning self-driving car is an instance of Phillipa Foot's trolley problem, 
in which a bystander watching a runaway trolley can pull a lever to kill one instead of three \citep{foot}. 
Decades of philosophical debate have developed ethical theories that can offer nuanced and 
consistent answers to the trolley problem. Like the trolley problem, the moral dilemmas 
that artifical agents face are not entirely new, so solutions to these problems should take advantage of philosophical 
progress. Ethical philosophers are devoted to the creation of better ethical theories, so the 
more faithful that automated ethics is to philosophical literature, the more nuanced, precise, consistent, and
therefore trustworthy it will be.

A lack of engagement with prior philosophical literature also makes automated moral agents less 
explainable, or interpretable by human observers. One example of this is Delphi, an implementation of automated ethics that uses deep 
learning to make moral judgements based on a training dataset of ethical decisions made by humans \citep{delphi}. 
Early versions of Delphi gave unexpected results, such as declaring that the user should commit 
genocide if it makes everyone happy \citep{verge}. Moreover, because no explicit ethical theory underpins 
Delphi's judgements, human beings cannot analytically determine why Delphi thinks genocide is obligatory
or where its reasoning may have gone wrong. 
Machine learning approaches like Delphi often cannot explain their decisions to a human being, reducing
human trust in a machine's controversial ethical judgements. If a machine prescribes killing one person 
to save three without rigorously justifying this decision, it is difficult to trust this judgement. 
The high stakes of automated ethics require explainability to build trust and catch mistakes, which
motivates philosophically faithful automated ethics.

@@

\item In Section \ref{computationalethics}, I present ethical insights discovered using my system and argue that
computational methods like the one presented in this thesis can help philosophers resolve debates about ethics.
Not only can my system help machines reason about ethics, but it can also help philosophers make philosophical
progress, just as computational tools unlock discoveries in fields like protein folding and drug discovery.
In Section \ref{ordinarypeople}, I extend this argument to the everyday ethical reasoning that we all
perform as we navigate the world and explore how automated ethics can improve our decision-making. 
\end{enumerate}%
\end{isamarkuptext}\isamarkuptrue%
%
\begin{isamarkuptext}%
\noindent \textbf{Automated Kantian Ethics}

@@

A machine that can evaluate the moral status of an action can not only help machines better reason about ethics, 
but it can also help philosophers better study philosophy. I argue for ``computational ethics,'' or the use of computational tools to 
make philosophical progress, analogous to computational biology. 
I demonstrate the potential of computational ethics by presenting a 
philosophical insight about which kinds of actions are appropriate for ethical consideration that I 
discovered using my system. The process of building and interacting with a computer that can reason 
about ethics helped me, a human philosopher, arrive at a philosophical conclusion that has implications for practical
reason and philosophy of doubt. Thus, my system can be used in three distinct ways. First, my system can help
automated agents navigate the world, which I will refer to as automated ethics or machine ethics interchangeably. Second, 
my system help human philosophers reason about philosophy, which I call computational ethics. Third, as 
I discuss in Section \ref{ordinarypeople}, computational ethics can help not only professional philosophers,
but can also augment the everyday ethical reasoning that we all perform as we navigate the world.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimtheory
%
\endisadelimtheory
%
\isatagtheory
%
\endisatagtheory
{\isafoldtheory}%
%
\isadelimtheory
%
\endisadelimtheory
%
\end{isabellebody}%
\endinput
%:%file=~/Desktop/cs91r/paper/thesis_1_intro.thy%:%
%:%24=6%:%
%:%36=8%:%
%:%37=9%:%
%:%38=10%:%
%:%39=11%:%
%:%40=12%:%
%:%41=13%:%
%:%42=14%:%
%:%43=15%:%
%:%44=16%:%
%:%45=17%:%
%:%46=18%:%
%:%47=19%:%
%:%48=20%:%
%:%49=21%:%
%:%50=22%:%
%:%51=23%:%
%:%52=24%:%
%:%53=25%:%
%:%54=26%:%
%:%55=27%:%
%:%56=28%:%
%:%57=29%:%
%:%58=30%:%
%:%59=31%:%
%:%60=32%:%
%:%61=33%:%
%:%62=34%:%
%:%63=35%:%
%:%64=36%:%
%:%65=37%:%
%:%66=38%:%
%:%67=39%:%
%:%68=40%:%
%:%69=41%:%
%:%70=42%:%
%:%71=43%:%
%:%72=44%:%
%:%73=45%:%
%:%74=46%:%
%:%75=47%:%
%:%76=48%:%
%:%77=49%:%
%:%78=50%:%
%:%79=51%:%
%:%80=52%:%
%:%81=53%:%
%:%82=54%:%
%:%83=55%:%
%:%84=56%:%
%:%85=57%:%
%:%86=58%:%
%:%87=59%:%
%:%88=60%:%
%:%89=61%:%
%:%90=62%:%
%:%91=63%:%
%:%92=64%:%
%:%93=65%:%
%:%94=66%:%
%:%95=67%:%
%:%96=68%:%
%:%97=69%:%
%:%98=70%:%
%:%99=71%:%
%:%100=72%:%
%:%101=73%:%
%:%102=74%:%
%:%103=75%:%
%:%104=76%:%
%:%105=77%:%
%:%106=78%:%
%:%107=79%:%
%:%108=80%:%
%:%109=81%:%
%:%110=82%:%
%:%111=83%:%
%:%112=84%:%
%:%113=85%:%
%:%114=86%:%
%:%115=87%:%
%:%116=88%:%
%:%120=91%:%
%:%121=92%:%
%:%122=93%:%
%:%123=94%:%
%:%124=95%:%
%:%125=96%:%
%:%126=97%:%
%:%127=98%:%
%:%128=99%:%
%:%129=100%:%
%:%130=101%:%
%:%131=102%:%
%:%132=103%:%
%:%133=104%:%
%:%134=105%:%
%:%135=106%:%
%:%136=107%:%
%:%137=108%:%
%:%138=109%:%
%:%139=110%:%
%:%140=111%:%
%:%141=112%:%
%:%142=113%:%
%:%143=114%:%
%:%144=115%:%
%:%145=116%:%
%:%149=119%:%
%:%150=120%:%
%:%151=121%:%
%:%152=122%:%
%:%153=123%:%
%:%154=124%:%
%:%155=125%:%
%:%156=126%:%
%:%157=127%:%
%:%158=128%:%
%:%159=129%:%
%:%160=130%:%
%:%161=131%:%
%:%162=132%:%
%:%163=133%:%
%:%164=134%:%
%:%165=135%:%
%:%166=136%:%
%:%167=137%:%
%:%168=138%:%
%:%169=139%:%
%:%170=140%:%
%:%171=141%:%
%:%172=142%:%
%:%173=143%:%
%:%174=144%:%
%:%175=145%:%
%:%176=146%:%
%:%177=147%:%
%:%178=148%:%
%:%179=149%:%
%:%180=150%:%
%:%181=151%:%
%:%182=152%:%
%:%183=153%:%
%:%184=154%:%
%:%185=155%:%
%:%186=156%:%
%:%187=157%:%
%:%188=158%:%
%:%189=159%:%
%:%190=160%:%
%:%191=161%:%
%:%192=162%:%
%:%193=163%:%
%:%194=164%:%
%:%195=165%:%
%:%196=166%:%
%:%197=167%:%
%:%198=168%:%
%:%199=169%:%
%:%200=170%:%
%:%201=171%:%
%:%202=172%:%
%:%203=173%:%
%:%204=174%:%
%:%205=175%:%
%:%206=176%:%
%:%207=177%:%
%:%208=178%:%
%:%209=179%:%
%:%210=180%:%
%:%211=181%:%
%:%212=182%:%
%:%213=183%:%
%:%214=184%:%
%:%215=185%:%
%:%216=186%:%
%:%217=187%:%
%:%218=188%:%
%:%219=189%:%
%:%220=190%:%

>>>>

%
\begin{isabellebody}%
\setisabellecontext{thesis{\isacharunderscore}{\isadigit{1}}{\isacharunderscore}intro}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isatagtheory
%
\endisatagtheory
{\isafoldtheory}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsection{Introduction\label{intro}%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
As AI becomes more sophisticated and less dependent on humans, interest begins to mount
in the development of automated moral agents, or computers that can perform ethical reasoning. 
AI is making decisions in increasingly 
consequential contexts, such as healthcare, driving, and criminal sentencing, and therefore 
must perform ethical reasoning in order to navigate moral dilemmas. For example, self-driving
cars may face less extreme versions of the following moral dilemma: an autonomous vehicle approaching 
an intersection fails to notice pedestrians in the crosswalk until it is too late to brake. The car 
can either continue on its course, running over and killing three pedestrians, or it can swerve to 
hit the car in the next lane, killing the single passenger inside it. While this example is (hopefully) 
not typical of the operation of a self-driving car, every decision that such an AI system makes, from 
avoiding congested freeways to carpooling, is morally tinged. Not only does AI routinely make decisions with 
ethical implications without explicitly performing ethical
reasoning, it often does so without human supervision. For example, the Allegheny Family Screening 
Tool can automatically trigger an investigation into a potential case of child neglect, a decision that 
can uproot entire families and is known to be biased against poor people of color \citep{eubanks}. 
This motivates the need for automated ethics (also called machine ethics), 
or the development of machines that can perform robust, sophisticated ethical reasoning.

Machine ethicists recognize the need for automated ethics and have made both theoretical 
(\citep{moralmachine}, \citep{davenport}, \citep{moralmachineonline}, \citep{gabriel}) and practical progress 
(\citep{logicprogramming}, \citep{biology}, \citep{winfield}, \citep{delphi}) towards automating ethics. 
However, prior work in machine ethics using popular ethical theories like deontology (\citep{deon1}, \citep{deon2}), 
consequentialism (\citep{util2}, \citep{cloos}, \citep{util1}), and virtue ethics \citep{virtue2} rarely 
engages with philosophical literature and thus often misses philosophers' insights. Even the above example of 
the malfunctioning self-driving car is an instance of Phillipa Foot's trolley problem, 
in which a bystander watching a runaway trolley can pull a lever to kill one instead of three \citep{foot}. 
Decades of philosophical debate have developed ethical theories that can offer nuanced and 
consistent answers to the trolley problem. Like the trolley problem, the moral dilemmas 
that artifical agents face are not entirely new, so solutions to these problems should take advantage of philosophical 
progress. Moral philosophers are devoted to the creation of better ethical theories, so the 
more faithful that automated ethics is to philosophical literature, the more nuanced, precise, consistent, and
therefore trustworthy it will be.

A lack of engagement with prior philosophical literature also makes automated ethics less 
explainable, or interpretable by human observers. One example of this is Delphi, an implementation of automated ethics that uses deep 
learning to make moral judgements based on a training dataset of ethical decisions made by humans \citep{delphi}. 
Early versions of Delphi gave unexpected results, such as declaring that the user should commit 
genocide if it makes everyone happy \citep{verge}. Moreover, because no explicit ethical theory underpins 
Delphi's judgements, human beings cannot analytically determine why Delphi thinks genocide is obligatory
or where its reasoning may have gone wrong. 
Machine learning approaches like Delphi often cannot explain their decisions to a human being, reducing
human trust in a machine's controversial ethical judgements. If a machine prescribes killing one person 
to save three without rigorously justifying this decision, it is difficult to trust this judgement. 
The high stakes of automated ethics require explainability to build trust and catch mistakes, which
motivates philosophically faithful automated ethics.

@@

\item In Section \ref{computationalethics}, I present ethical insights discovered using my system and argue that
computational methods like the one presented in this thesis can help philosophers resolve debates about ethics.
Not only can my system help machines reason about ethics, but it can also help philosophers make philosophical
progress, just as computational tools unlock discoveries in fields like protein folding and drug discovery.
In Section \ref{ordinarypeople}, I extend this argument to the everyday ethical reasoning that we all
perform as we navigate the world and explore how automated ethics can improve our decision-making. 
\end{enumerate}%
\end{isamarkuptext}\isamarkuptrue%
%
\begin{isamarkuptext}%
\noindent \textbf{Automated Kantian Ethics: An Overview}

@@

A machine that can evaluate the moral status of an action can not only help machines better reason about ethics, 
but it can also help philosophers better study philosophy. I argue for ``computational ethics,'' or the use of computational tools to 
make philosophical progress, analogous to computational biology. 
I demonstrate the potential of computational ethics by presenting a 
philosophical insight about which kinds of actions are appropriate for ethical consideration that I 
discovered using my system. The process of building and interacting with a computer that can reason 
about ethics helped me, a human philosopher, arrive at a philosophical conclusion that has implications for practical
reason and philosophy of doubt. Thus, my system can be used in three distinct ways. First, my system can help
automated agents navigate the world, which I will refer to as automated ethics or machine ethics interchangeably. Second, 
my system help human philosophers reason about philosophy, which I call computational ethics. Third, as 
I discuss in Section \ref{ordinarypeople}, computational ethics can help not only professional philosophers,
but can also augment the everyday ethical reasoning that we all perform as we navigate the world.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimtheory
%
\endisadelimtheory
%
\isatagtheory
%
\endisatagtheory
{\isafoldtheory}%
%
\isadelimtheory
%
\endisadelimtheory
%
\end{isabellebody}%
\endinput
%:%file=~/Desktop/cs91r/paper/thesis_1_intro.thy%:%
%:%24=6%:%
%:%36=8%:%
%:%37=9%:%
%:%38=10%:%
%:%39=11%:%
%:%40=12%:%
%:%41=13%:%
%:%42=14%:%
%:%43=15%:%
%:%44=16%:%
%:%45=17%:%
%:%46=18%:%
%:%47=19%:%
%:%48=20%:%
%:%49=21%:%
%:%50=22%:%
%:%51=23%:%
%:%52=24%:%
%:%53=25%:%
%:%54=26%:%
%:%55=27%:%
%:%56=28%:%
%:%57=29%:%
%:%58=30%:%
%:%59=31%:%
%:%60=32%:%
%:%61=33%:%
%:%62=34%:%
%:%63=35%:%
%:%64=36%:%
%:%65=37%:%
%:%66=38%:%
%:%67=39%:%
%:%68=40%:%
%:%69=41%:%
%:%70=42%:%
%:%71=43%:%
%:%72=44%:%
%:%73=45%:%
%:%74=46%:%
%:%75=47%:%
%:%76=48%:%
%:%77=49%:%
%:%78=50%:%
%:%79=51%:%
%:%80=52%:%
%:%81=53%:%
%:%82=54%:%
%:%83=55%:%
%:%84=56%:%
%:%85=57%:%
%:%86=58%:%
%:%87=59%:%
%:%88=60%:%
%:%89=61%:%
%:%90=62%:%
%:%91=63%:%
%:%92=64%:%
%:%93=65%:%
%:%94=66%:%
%:%95=67%:%
%:%96=68%:%
%:%97=69%:%
%:%98=70%:%
%:%99=71%:%
%:%100=72%:%
%:%101=73%:%
%:%102=74%:%
%:%103=75%:%
%:%104=76%:%
%:%105=77%:%
%:%106=78%:%
%:%107=79%:%
%:%108=80%:%
%:%109=81%:%
%:%110=82%:%
%:%111=83%:%
%:%112=84%:%
%:%113=85%:%
%:%114=86%:%
%:%115=87%:%
%:%116=88%:%
%:%117=89%:%
%:%118=90%:%
%:%122=93%:%
%:%123=94%:%
%:%124=95%:%
%:%125=96%:%
%:%126=97%:%
%:%127=98%:%
%:%128=99%:%
%:%129=100%:%
%:%130=101%:%
%:%131=102%:%
%:%132=103%:%
%:%133=104%:%
%:%134=105%:%
%:%135=106%:%
%:%136=107%:%
%:%137=108%:%
%:%138=109%:%
%:%139=110%:%
%:%140=111%:%
%:%141=112%:%
%:%142=113%:%
%:%143=114%:%
%:%144=115%:%
%:%145=116%:%
%:%146=117%:%
%:%147=118%:%
%:%151=121%:%
%:%152=122%:%
%:%153=123%:%
%:%154=124%:%
%:%155=125%:%
%:%156=126%:%
%:%157=127%:%
%:%158=128%:%
%:%159=129%:%
%:%160=130%:%
%:%161=131%:%
%:%162=132%:%
%:%163=133%:%
%:%164=134%:%
%:%165=135%:%
%:%166=136%:%
%:%167=137%:%
%:%168=138%:%
%:%169=139%:%
%:%170=140%:%
%:%171=141%:%
%:%172=142%:%
%:%173=143%:%
%:%174=144%:%
%:%175=145%:%
%:%176=146%:%
%:%177=147%:%
%:%178=148%:%
%:%179=149%:%
%:%180=150%:%
%:%181=151%:%
%:%182=152%:%
%:%183=153%:%
%:%184=154%:%
%:%185=155%:%
%:%186=156%:%
%:%187=157%:%
%:%188=158%:%
%:%189=159%:%
%:%190=160%:%
%:%191=161%:%
%:%192=162%:%
%:%193=163%:%
%:%194=164%:%
%:%195=165%:%
%:%196=166%:%
%:%197=167%:%
%:%198=168%:%
%:%199=169%:%
%:%200=170%:%
%:%201=171%:%
%:%202=172%:%
%:%203=173%:%
%:%204=174%:%
%:%205=175%:%
%:%206=176%:%
%:%207=177%:%
%:%208=178%:%
%:%209=179%:%
%:%210=180%:%
%:%211=181%:%
%:%212=182%:%
%:%213=183%:%
%:%214=184%:%
%:%215=185%:%
%:%216=186%:%
%:%217=187%:%
%:%218=188%:%
%:%219=189%:%
%:%220=190%:%
%:%221=191%:%
%:%222=192%:%
